---
title: "R code for 'Apparent physiological costs of blood parasite infection in the early-life of a vertebrate host - only in highest infections'"
author: "Tony Rinaud, Meinolf Ottensmann, Oliver Krüger & Nayden Chakarov"
output: html_document
---

This document provides all the `R code` used in our paper. Both the Rmarkdown file and the data can be downloaded from the accompanying GitHub repository on (<https://github.com/TonyRinaud/MS_physiology_infection>) as a zip archive containing all the files. We recommend to download or clone this [GitHub repository](https://github.com/TonyRinaud/MS_physiology_infection) in order to access the documentation together with all the files that are needed to repeat analyses shown in this document. Just click on the link above and then on the green box `Clone or download`. In order to function properly, the same structure of folders must be kept. If you have any questions, don't hesitate to contact [tony.rinaud\@gmail.com](mailto:tony.rinaud@gmail.com){.email}

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 8, fig.height = 8, comment = "#>",
  echo = TRUE, strip.white = TRUE, collapse = TRUE, fig.align = "center",
  warning = F, message = F, highlight = TRUE, tidy = TRUE)
```

## Required packages

A number of packages, all of which are available on CRAN are required to repeat analyses presented in this document. The code chunk below allows to load them for the analyses. Any missing package needs to be installed before, using the 'install.packages())' function:

```{r packages, message=F, warning=F}
library(chron)
library(cowplot)
library(EnvStats)
library(lme4)
library(lmerTest)
library(lsmeans)
library(ggalt)
library(ggdist)
library(ggeffects)
library(ggplot2)
library(ggpubr)
library(ggrepel)
library(ggridges)
library(ggsci)
library(ggsignif)
library(grid)
library(gridExtra)
library(magrittr)
library(patchwork)
library(plyr)
library(rptR)
library(RVAideMemoire)
library(sjPlot)
library(sjlabelled)
library(sjmisc)
library(tidybayes)
library(tidyverse)
library(wesanderson)
library(car)
## set theme for ggplot objects
theme_set(theme_tidybayes() + panel_border())
```

## Load raw data

The raw data is comprised of 276 common buzzard (*Buteo buteo*) individuals. Each individual was sampled twice over the course of the nestling period during the years 2016 and 2018 - 2020. First, the raw data is loaded from the file `physiology_infection_stage_full_wideformat.csv` and re-formatted (scaling variables, reordering factor levels etc.) before downstream analyses:

```{r data}
## Load data from csv file and code variable classes
## -----------------------------------------------------------------------------
df <- 
  read.csv('./physiology_infection_stage_full_wideformat.csv', h = T, sep = ';', dec = ".") %>% 
  mutate(Nest = as.factor(Nest)) %>% 
  mutate(Date = chron(as.character(Date), format = "d/m/y")) %>% 
  mutate(Infection_intensity.1 = as.factor(Infection_intensity.1)) %>% 
  mutate(Infection_intensity.2 = as.factor(Infection_intensity.2)) %>%
  mutate(Prevalence2 = as.factor(ifelse(Infection_intensity.2 == 0, 0, 1))) %>%
  mutate(Prevalence1 = as.factor(ifelse(Infection_intensity.1 == 0, 0, 1))) %>% 
  mutate(Breathing_rate = as.numeric(Breathing_rate)) %>% 
  mutate(Sex = as.factor(Sex)) %>% 
  mutate(Sampling_rank = as.factor(Sampling_rank)) %>% 
  mutate(Weight_g = scale(as.numeric(Weight.2))) %>% 
  mutate(Wing_cm = as.numeric(Wing.2)) %>% 
  mutate(body_temperature = as.numeric(body_temperature)) %>% 
  mutate(delta_body_condition = as.numeric(delta_body_condition)) %>% 
  mutate(Ambient_Temperature_AvgC = scale(as.numeric(TemperatureAvgC))) %>% 
  mutate(Treatment = as.factor(Treatment)) %>% 
  mutate(Year = as.factor(Year)) %>% 
  mutate(Growth_rate = as.numeric(Growth_rate)) %>% 
  mutate(days_resample = scale(days_resample)) %>% 
  mutate(Age_in_days = scale(as.numeric(Age_in_days))) %>% 
  mutate(intensity_change = as.numeric(intensity_change)) %>% 
  mutate(Diff_Inf_Class = factor(Diff_Inf_Class, levels = c("Uninfected","Increase","Peak","Decrease")))
 
## Arrange data frame
## ----------------------------------------------------------------------------- 
df <- arrange(df, df$Diff_Inf_Class)
```

## Effects on parasites

Investigating treatment (*control* vs *Malarone*) effects on the prevalence of *Leucocytozoon* parasites:

```{r, results='hide', message=F, warning=F,prompt=F}
## Build contingency table: Infection prevalence and treatment: First sampling
## -----------------------------------------------------------------------------
pre_treatment <- with(df, table(Prevalence1, Treatment))
prop.test(pre_treatment)
pairwise.prop.test(pre_treatment)

## Build contingency table: Infection prevalence and treatment: Second sampling
## -----------------------------------------------------------------------------
post_treatment <- with(df, table(Prevalence2, Treatment))
prop.test(post_treatment)
pairwise.prop.test(post_treatment)

## Proportion of infected individuals across time points
## -----------------------------------------------------------------------------
infected_treatment <- 
  matrix(c(pre_treatment[2,], post_treatment[2,]), nrow = 2) %>% 
  set_colnames(., c("Pre", "Post")) %>% 
  set_rownames(., c("Control", "Malarone"))
prop.test(infected_treatment)
pairwise.prop.test(infected_treatment)

## Proportion of uninfected individuals across time points
## -----------------------------------------------------------------------------
uninfected_treatment <- 
  matrix(c(pre_treatment[1,], post_treatment[1,]), nrow = 2) %>% 
  set_colnames(., c("Pre", "Post")) %>% 
  set_rownames(., c("Control", "Malarone"))
prop.test(uninfected_treatment)
pairwise.prop.test(uninfected_treatment)


## Plotting count of infected / uninfected nestlings across treatments
## -----------------------------------------------------------------------------
tab_cont = data.frame(
  Count = c(infected_treatment[1,], uninfected_treatment[1,], infected_treatment[2,], uninfected_treatment[2,]),
  Timepoint = rep(c("First sampling","Second sampling"), 4),
  Treatment = rep(c("Control", "Treatment"), each = 4),
  Prevalence = rep(rep(c("Infected", "Uninfected"), each = 2),2)) %>% 
  mutate(Timepoint = factor(Timepoint, levels = c("First sampling","Second sampling"))) %>% 
  mutate(Prevalence = factor(Prevalence, levels = c("Uninfected","Infected")))
    
##  Create Figure 2a
## -----------------------------------------------------------------------------
Fig_2A  <- ggplot(tab_cont) +  
  aes(Timepoint, Count, fill = Prevalence) +  
  facet_wrap(facets = "Treatment") +  
  geom_bar(stat = 'identity',  width = 0.3) +  
  labs(y = "Count of nestlings") +  
  geom_text(aes(label = Count),position  = position_stack(0.5),size=5) +  
  scale_fill_manual(values = c("#D0D0D0","#A8A8A8")) + 
  scale_x_discrete(labels = c("First\nsampling","Second\nsampling","First\nsampling","Second\nsampling"))+  
  theme(axis.title.x  =  element_blank(), 
        strip.text = element_text(size = 26, face = "bold"),
        legend.text = element_text(size = 24),
        legend.title = element_blank(),
        legend.position = c(0.85, 0.90),
        axis.title.y = element_text(size = 28, margin =  unit(c(0, 3, 0, 0), "mm")),
        axis.text.x = element_text(size = 24, margin =  unit(c(3, 0, 0, 0), "mm")),
        axis.text.y = element_text(size = 24, margin =  unit(c(0, 1, 0, 0), "mm")))

## Plotting mean infection intensity values of nestlings across treatments
## -----------------------------------------------------------------------------
mean_infint = data.frame(
  Sampling_rank = factor(c(rep("1",length(df$Sampling_rank)),as.character(df$Sampling_rank)),levels = c("1","2"),
                         labels  =  c("First sampling","Second sampling")),
  Infection_intensity = as.numeric(c(as.character(df$Infection_intensity.1),as.character(df$Infection_intensity.2))),
  Treatment = factor(c(as.character(rep(df$Treatment,2))),levels  =  c("Control","Malarone")))

## Figure 2b
## -----------------------------------------------------------------------------
Fig_2B <- ggplot(mean_infint) +
  aes(Sampling_rank, Infection_intensity, group = Treatment) +
  geom_vline(xintercept  =  "First sampling", linetype = "dashed", color = 'darkgrey') +
  geom_vline(xintercept = "Second sampling", linetype = "dashed", color = 'darkgrey') +
  labs(y = "Mean infection intensity") +
  geom_point(aes(colour = Treatment),position = position_jitterdodge(jitter.height  =  0.1)) +
  stat_summary(fun = mean, geom = "line",size = 2,color = c("lightgrey","black","black","lightgrey")) + 
  scale_x_discrete(labels = c("First\nsampling","Second\nsampling"))+
  stat_summary(fun = mean, geom = "point",size = 5) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.04, size = 2) + 
  scale_color_manual(values = c("lightgrey","black")) + 
  theme(axis.title.x = element_blank(),
        legend.text = element_text(size = 24),
        legend.title = element_text(size = 26),
        axis.title.y = element_text(size = 28, margin =  unit(c(0, 5, 0, 0), "mm")),
        axis.text.x = element_text(size = 26, margin =  unit(c(3, 0, 0, 0), "mm")),
        axis.text.y = element_text(size = 26, margin =  unit(c(0, 1, 0, 3), "mm")),
        plot.margin = unit(c(0,0,0,30), "pt"))

## Panel wrapping Fig2 a & b:
## ----------------------------------------------------------------------------- 
Fig2 <-  Fig_2A +Fig_2B+
  plot_annotation(tag_levels = 'a') + 
  theme(plot.tag = element_text(size = 22, face = "bold"))

Fig_2A
Fig_2B

ggsave(Fig2,filename = "./Figs/Fig2_efficiency_malarone.png",units = "px", width = 6000, height = 3000)


## Testing for difference in parasitic load between Treatment groups at first sampling
## -----------------------------------------------------------------------------

perm.t.test(as.numeric(as.character(df$Infection_intensity.1))~df$Treatment, progress = F)

## Testing for Treatment effect on parasitemia change between first and second sampling
## Note: 
## intensity change -100 codes for individuals that were uninfected throughout 
## the experiment!
## -----------------------------------------------------------------------------
lmerTest::lmer(intensity_change ~ Treatment + Year + days_resample + (1|Nest), 
               data = df[!df$intensity_change %in% -100,]) %>%
  summary()
```

## Infection stages as explanatory variable 

Exploring differences in physiological measures that are associated with the infection stage (increase, peak or decreasing) of tested individuals. All models account for a number of fixed effects and non-independence among nest mates. 

### Breathing rate


```{r mixed model breathing rate}
## Run model
## ----------------------------------------------------------------------------- 
lmer_br <- lmer(
  Breathing_rate ~ Diff_Inf_Class + Diff_Inf_Class:Treatment + 
    days_resample + Age_in_days + Weight_g + Sex + Ambient_Temperature_AvgC + Year + (1|Nest),
  data = df)

## Obtain predicted values for each infection stage
## -----------------------------------------------------------------------------
mod_br <- get_model_data(lmer_br, type = 'pred', terms = "Diff_Inf_Class") %>% 
   mutate(x = factor(c("Uninfected","Increase","Peak","Decrease"), 
                     levels = c("Uninfected","Increase","Peak","Decrease")))

## Extract sample size for infection stage
## -----------------------------------------------------------------------------
n <- table(df$Diff_Inf_Class[!is.na(df$Breathing_rate)])

## ad sample size as label
## -----------------------------------------------------------------------------
mod_br <- mod_br %>% 
  mutate(x = factor(c(paste0(x,"\nn= ",n)), levels = c(paste0(x,"\nn= ",n))))

## Plotting predicted values across infection stages
## -----------------------------------------------------------------------------
Fig_S1A <- ggplot(mod_br) + 
  aes(x,predicted) + 
  geom_hline(yintercept = mean(mod_br$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Breathing rate") + 
  ylim(c(min(mod_br$conf.low) - 1.5,max(mod_br$conf.high) + 1.5)) + 
  geom_errorbar(aes(ymin = mod_br$conf.low,ymax = mod_br$conf.high),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_br$predicted - mod_br$std.error, ymax = mod_br$predicted + mod_br$std.error),
                size = 8, colour = wes_palette("Zissou1",4), width = 0,) + 
  geom_point(color = "black", outlier.shape = NA, size = 2, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 16),
        axis.line.x = element_blank(), 
        axis.ticks.x = element_blank(), 
        plot.margin = margin(0, 0, 0, 0, "cm"), 
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8,
  aes(x = 1, y = max(mod_br$conf.high) + 1, xend = 4, yend = max(mod_br$conf.high) + 1)) + 
  geom_text(aes(x = 2.5, y = max(mod_br$conf.high) + 1.5),
  label = "n.s.", size = 5)
```

### Body temperature

```{r mixed model body temp}
## Model 
## -----------------------------------------------------------------------------
lmer_bt = lmer(
  body_temperature ~ Diff_Inf_Class + Diff_Inf_Class:Treatment + Ambient_Temperature_AvgC + 
    days_resample + Age_in_days + Weight_g + Sex + Year + (1|Nest),
  data = df)

## Predicted values for each infection stage
## -----------------------------------------------------------------------------
mod_bt = get_model_data(lmer_bt,type = 'pred',terms = "Diff_Inf_Class") %>%
  mutate(x = factor(c("Uninfected","Increase","Peak","Decrease"),
                    levels = c("Uninfected","Increase","Peak","Decrease")))

# Table with sample sizes specific for body temperature data
n2 = table(df$Diff_Inf_Class[!is.na(df$body_temperature)])

mod_bt <- mod_bt %>% 
  mutate(x = factor(c(paste0(x,"\nn= ",n2)), levels = c(paste0(x,"\nn= ",n2))))

# Plotting predicted values across infection stages
Fig_S1B <- ggplot(mod_bt) + 
  aes(x,predicted) + 
  geom_hline(yintercept = mean(mod_bt$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Body temperature") + 
  geom_errorbar(aes(ymin = mod_bt$conf.low,ymax = mod_bt$conf.high),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_bt$predicted - mod_bt$std.error,ymax = mod_bt$predicted + mod_bt$std.error),
                size = 8,colour = wes_palette("Zissou1",4), width = 0) + 
  geom_point(color = "black", outlier.shape = NA, size = 2, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title.y = element_text(size = 18, margin = unit(c(0,3,0,0),"mm")), 
        axis.text = element_text(size = 16),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8,
                 aes(x = 1, y = 40.6, xend = 4, yend = 40.6)) + 
    geom_text(aes(x = 2.5, y = 40.7),
              label = "n.s.", size = 5)
```

### Body condition change

```{r mixed model body condition}
## Model 
## -----------------------------------------------------------------------------
lmer_bc <- lmer(
  delta_body_condition ~ Diff_Inf_Class+Diff_Inf_Class:Treatment+days_resample + 
    Age_in_days+Sex+Year+(1|Nest),
  data = df)

# Predicted values for each infection stage
mod_bc = get_model_data(lmer_bc,type = 'pred',terms = "Diff_Inf_Class") %>%
  mutate(x = factor(c("Uninfected","Increase","Peak","Decrease"), 
                  levels = c("Uninfected","Increase","Peak","Decrease")))

# Table with sample sizes specific for body condition change data
n3 = table(df$Diff_Inf_Class[!is.na(df$delta_body_condition)])

mod_bc <- mod_bc %>% 
  mutate(x = factor(c(paste0(x,"\nn= ",n3)), levels = c(paste0(x,"\nn= ",n3))))

# Plotting predicted values across infection stages

Fig_S1C = ggplot(mod_bc) + 
  aes(x,predicted) + 
  geom_hline(yintercept = mean(mod_bc$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Δ Body condition") + 
  geom_errorbar(aes(ymin = mod_bc$conf.low,ymax = mod_bc$conf.high),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_bc$predicted - mod_bc$std.error,ymax = mod_bc$predicted + mod_bc$std.error),
                size = 8,colour = wes_palette("Zissou1",4), width = 0,) + 
  geom_point(color = "black", outlier.shape = NA, size = 2, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 16),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8, aes(x = 1, y = max(mod_bc$conf.high) + 17, xend = 4, yend = max(mod_bc$conf.high) + 17)) + 
  geom_text(aes(x = 2.5, y = max(mod_bc$conf.high) + 23),
              label = "n.s.", size = 5)
```

### Growth rate

```{r mixed model growth rate}
# Model 
lmer_gr = lmer(Growth_rate ~ Diff_Inf_Class + Diff_Inf_Class:Treatment + Sex +
                 days_resample + Age_in_days + Year + (1|Nest), data = df)

# Predicted values for each infection stages
mod_gr = get_model_data(lmer_gr,type = 'pred',terms = "Diff_Inf_Class") %>%
  mutate(x = factor(c("Uninfected","Increase","Peak","Decrease"), levels = c("Uninfected","Increase","Peak","Decrease")))

# Table with sample sizes specific for growth rate data
n4 = table(df$Diff_Inf_Class[!is.na(df$Growth_rate)])

mod_gr <- mod_gr %>% 
  mutate(x = factor(c(paste0(x,"\nn= ",n4)), levels = c(paste0(x,"\nn= ",n4))))

# Plotting predicted values across infection stages

Fig_S1D = ggplot(mod_gr) + 
  aes(x,predicted) + 
  geom_hline(yintercept = mean(mod_gr$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Growth rate") + 
  geom_errorbar(aes(ymin = mod_gr$conf.low,ymax = mod_gr$conf.high),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_gr$predicted - mod_gr$std.error,ymax = mod_gr$predicted + mod_gr$std.error), 
                size = 8,colour = wes_palette("Zissou1",4), width = 0,) + 
  geom_point(color = "black", outlier.shape = NA, size = 2, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none", 
        axis.title.y = element_text(size = 18, margin = unit(c(0, 3, 0, 0), "mm")),
        axis.text = element_text(size = 16),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.margin = margin(0, 0, 0, 30, "pt"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8, aes(x = 1, y = max(mod_gr$conf.high) + 1.2, xend = 4, yend = max(mod_gr$conf.high) + 1.2)) + 
    geom_text(aes(x = 2.5, y = max(mod_gr$conf.high) + 2),
              label = "n.s.", size = 5)
```

## Summary four models

The code below is used to summarise the model output and creates Figure 4 and Table 3 as shown in the manuscript.

```{r}

# Table 1 and Table S3 
## -----------------------------------------------------------------------------
sjPlot::tab_model(
  lmer_br,lmer_bt,lmer_bc,lmer_gr,
  show.ci50 = T ,
  show.stat = T,
  string.stat = "t",
  df.method = "kr",
  show.df=T,
  dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
  file = "./Tables/Table1_results_lmer_physiological_parameters_p.val_kr.html")
```

## Parasitemia as explanatory variable

Exploration of effects by parasitemia levels on physiology of individuals. All models account for a number of fixed effects and non-independence among nest mates. 

### Breathing rate

```{r mixed model breathing rate 2}
## Model:
## Note: 
## One Contrast for the Interaction of Infection intensity and treatment
## is not estimatable due to the lack of infection level 4 for the Malarone-group
## -----------------------------------------------------------------------------
lmer_br_para = lmer(
  Breathing_rate ~ Infection_intensity.2 + Infection_intensity.2:Treatment + days_resample + 
    Age_in_days + Weight_g + Sex + Ambient_Temperature_AvgC + Year + (1|Nest), data = df)

## Rerun without intercept for plotting mean estimates 
## -----------------------------------------------------------------------------
lmer_br_para_no_intercept = lmer(
  Breathing_rate ~ 0 + Infection_intensity.2 + Infection_intensity.2:Treatment + days_resample + 
    Age_in_days + Weight_g + Sex + Ambient_Temperature_AvgC + Year + (1|Nest), data = df)

## Obtain effect sizes for post-treatment parasitemia and derive model predictions
## -----------------------------------------------------------------------------
mod_br_para <- 
  left_join(plot_model(lmer_br_para_no_intercept, se = F, )[["data"]][1:5,], ## 95% CI
            plot_model(lmer_br_para_no_intercept, se = T, )[["data"]][1:5,]) %>%  ## SE
  mutate(predicted = estimate) %>% 
  mutate(lower_CI = conf.low) %>% 
  mutate(higher_CI = conf.high) %>% 
  mutate(se = std.error) %>% 
  mutate(x = factor(c("0","1","2","3","4"), levels = c("0","1","2","3","4")))


## Obtain sample sizes for labels 
## ----------------------------------------------------------------------------- 
m1 = table(df$Infection_intensity.2[!is.na(df$Breathing_rate)])
mod_br_para <- mod_br_para %>% 
  mutate(x = factor(c(paste0(x,"\nn= ",m1)), levels = c(paste0(x,"\nn= ",m1))))

# Plotting predicted values across infection intensities
## -----------------------------------------------------------------------------
Fig_4A = ggplot(mod_br_para) + 
  aes(as.factor(mod_br_para$x),mod_br_para$predicted) + 
  geom_hline(yintercept = mean(mod_br_para$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Breathing rate") + 
  geom_errorbar(aes(ymin = mod_br_para$lower_CI,
                    ymax = mod_br_para$higher_CI),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_br_para$predicted - mod_br_para$se, 
                    ymax = mod_br_para$predicted + mod_br_para$se),
                size = 8, colour = wes_palette("Zissou1",5), width = 0,) + 
  geom_point(color = "black", size = 4) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 20),
        axis.text = element_text(size = 16),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8, aes(x = 1, y = max(mod_br_para$higher_CI, na.rm = T) + 1.2,
                              xend = 5, yend = max(mod_br_para$higher_CI, na.rm = T) + 1.2)) + 
    geom_text(aes(x = 3, y = max(mod_br_para$higher_CI, na.rm = T) + 2),
              label = "n.s.", size = 6)
```

### Body temperature

```{r  mixed model body temperature 2, warning=FALSE, message=F, echo=T}
## Model:
## Note: 
## One Contrast for the Interaction of Infection intensity and treatment
## is not estimatable due to the lack of infection level 4 for the Malarone-group
## -----------------------------------------------------------------------------
lmer_bt_para = lmer(
  body_temperature ~ Infection_intensity.2 + Infection_intensity.2:Treatment + days_resample +
    Ambient_Temperature_AvgC + Age_in_days + Weight_g + Sex + Year + (1|Nest), data = df)

## Rerun without intercept for plotting mean estimates 
## -----------------------------------------------------------------------------
lmer_bt_para_no_intercept = lmer(
  body_temperature ~ 0 + Infection_intensity.2 + Infection_intensity.2:Treatment + days_resample +
    Ambient_Temperature_AvgC + Age_in_days + Weight_g + Sex + Year + (1|Nest), data = df)

## Obtain effect sizes for post-treatment parasitemia and derive model predictions
## -----------------------------------------------------------------------------
mod_bt_para <- 
  left_join(plot_model(lmer_bt_para_no_intercept, se = F, )[["data"]][1:5,], ## 95% CI
            plot_model(lmer_bt_para_no_intercept, se = T, )[["data"]][1:5,]) %>%  ## SE
  mutate(predicted = estimate) %>% 
  mutate(lower_CI = conf.low) %>% 
  mutate(higher_CI = conf.high) %>% 
  mutate(se = std.error) %>% 
  mutate(x = factor(c("0","1","2","3","4"), levels = c("0","1","2","3","4")))

## Obtain sample sizes for labels 
## ----------------------------------------------------------------------------- 
m2 = table(df$Infection_intensity.2[!is.na(df$body_temperature)])
mod_bt_para <- mod_bt_para %>% 
  mutate(x = factor(c(paste0(x,"\nn= ",m2)), levels = c(paste0(x,"\nn= ",m2))))

## Plotting predicted values across infection intensities
## -----------------------------------------------------------------------------
Fig_4B = ggplot(mod_bt_para) + 
  aes(as.factor(mod_bt_para$x),mod_bt_para$predicted) + 
  geom_hline(yintercept = mean(mod_bt_para$predicted, na.rm = T), linetype = "dashed") + 
  geom_errorbar(aes(ymin = mod_bt_para$lower_CI,ymax = mod_bt_para$higher_CI),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_bt_para$predicted - mod_bt_para$se,ymax = mod_bt_para$predicted + mod_bt_para$se),
                size = 8,colour = wes_palette("Zissou1",5), width = 0,) + 
  labs(x = "", y = "Body temperature") + 
  geom_point(color = "black", size = 4) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 20),
        axis.text = element_text(size = 16),
        axis.line.x = element_blank(), 
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8, aes(x = 1, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.2,
                              xend = 5, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.2)) + 
  geom_text(aes(x = 3, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.3),
            label = "t = -2.80, df = 140, P = 0.006", size = 5) + 
  geom_segment(size = .8,
               aes(x = 1, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.2,
                   xend = 1, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.1)) + 
  geom_segment(size = .8,
               aes(x = 5, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.1,
                   xend = 5, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.2))
```

### Body condition change

```{r mixed model body condition change 2}
## Model:
## Note: 
## One Contrast for the Interaction of Infection intensity and treatment
## is not estimatable due to the lack of infection level 4 for the Malarone-group
## -----------------------------------------------------------------------------
lmer_bc_para <- lmer(
  delta_body_condition ~ Infection_intensity.2 + Infection_intensity.2:Treatment + days_resample +
    Age_in_days + Sex + Year + (1|Nest), data = df)

## Rerun without intercept for plotting mean estimates 
## -----------------------------------------------------------------------------
lmer_bc_para_no_intercept <- lmer(
  delta_body_condition ~ 0+ Infection_intensity.2 + Infection_intensity.2:Treatment + days_resample +
    Age_in_days + Sex + Year + (1|Nest), data = df)

## Obtain effect sizes for post-treatment parasitemia and derive model predictions
## -----------------------------------------------------------------------------
mod_bc_para <- 
  left_join(plot_model(lmer_bc_para_no_intercept, se = F, )[["data"]][1:5,], ## 95% CI
            plot_model(lmer_bc_para_no_intercept, se = T, )[["data"]][1:5,]) %>%  ## SE
  mutate(predicted = estimate) %>% 
  mutate(lower_CI = conf.low) %>% 
  mutate(higher_CI = conf.high) %>% 
  mutate(se = std.error) %>% 
  mutate(x = factor(c("0","1","2","3","4"), levels = c("0","1","2","3","4")))

# Table with sample sizes specific for body condition change data
m3 = table(df$Infection_intensity.2[!is.na(df$delta_body_condition)])
mod_bc_para <- mod_bc_para %>% 
  mutate(x = factor(c(paste0(x,"\nn= ",m3)), levels = c(paste0(x,"\nn= ",m3))))

# Plotting predicted values across infection intensities

Fig_4C = ggplot(mod_bc_para) + 
  aes(as.factor(mod_bc_para$x),mod_bc_para$predicted) + 
  geom_hline(yintercept = mean(mod_bc_para$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Δ Body condition") + 
  geom_errorbar(aes(ymin = mod_bc_para$lower_CI, ymax = mod_bc_para$higher_CI),
                colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_bc_para$predicted - mod_bc_para$se,
                    ymax = mod_bc_para$predicted + mod_bc_para$se),
                size = 8, colour = wes_palette("Zissou1",5), width = 0,) + 
  geom_point(color = "black", size = 4) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 20),  
        axis.text = element_text(size = 16), 
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8,
                 aes(x = 1, y = 60, xend = 5, yend = 60)) + 
    geom_text(aes(x = 3, y = 67),
              label = "t = -1.76, df = 247, P = 0.080", size = 5) + 
  geom_segment(size = .8,
                 aes(x = 1, y = 60, xend = 1, yend = 53)) + 
  geom_segment(size = .8,
                 aes(x = 5, y = 60, xend = 5, yend = 53))
```

### Growth rate

```{r mixed model growth rate 2}
## Model:
## Note: 
## One Contrast for the Interaction of Infection intensity and treatment
## is not estimatable due to the lack of infection level 4 for the Malarone-group
## -----------------------------------------------------------------------------
lmer_gr_para = lmer(
  Growth_rate ~ Infection_intensity.2 + Infection_intensity.2:Treatment +
    days_resample + Sex + Age_in_days + Year + (1 | Nest), data = df)

## Rerun without intercept for plotting mean estimates 
## -----------------------------------------------------------------------------
lmer_gr_para_no_intercept  = lmer(
  Growth_rate ~ 0 + Infection_intensity.2 + Infection_intensity.2:Treatment +
    days_resample + Sex + Age_in_days + Year + (1 | Nest), data = df)

## Obtain effect sizes for post-treatment parasitemia and derive model predictions
## -----------------------------------------------------------------------------
mod_gr_para <- 
  left_join(plot_model(lmer_gr_para_no_intercept, se = F, )[["data"]][1:5,], ## 95% CI
            plot_model(lmer_gr_para_no_intercept, se = T, )[["data"]][1:5,]) %>%  ## SE
  mutate(predicted = estimate) %>% 
  mutate(lower_CI = conf.low) %>% 
  mutate(higher_CI = conf.high) %>% 
  mutate(se = std.error) %>% 
  mutate(x = factor(c("0","1","2","3","4"), levels = c("0","1","2","3","4")))

# Table with sample sizes specific for growth rate data
m4 = table(df$Infection_intensity.2[!is.na(df$Growth_rate)])

mod_gr_para <- mod_gr_para %>% 
  mutate(x = factor(c(paste0(x,"\nn= ",m4)), levels = c(paste0(x,"\nn= ",m4))))

# Plotting predicted values across infection intensities
## -----------------------------------------------------------------------------
Fig_4D = ggplot(mod_gr_para) + 
  aes(as.factor(mod_gr_para$x),mod_gr_para$predicted) + 
  geom_hline(yintercept = mean(mod_gr_para$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Growth rate") + 
  geom_errorbar(aes(ymin = mod_gr_para$lower_CI,
                    ymax = mod_gr_para$higher_CI), colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_gr_para$predicted - mod_gr_para$se,
                    ymax = mod_gr_para$predicted + mod_gr_para$se),size = 8, 
                colour = wes_palette("Zissou1",5), width = 0) + 
  geom_point(color = "black", outlier.shape = NA, size = 4, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none", 
        axis.title = element_text(size = 20),
        axis.text = element_text(size = 16),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8,
               aes(x = 1, y = 30, xend = 5, yend = 30)) + 
  geom_text(aes(x = 3, y = 31),
            label = "t = 2.06, df = 258, P = 0.094", size = 5) + 
  geom_segment(size = .8,
               aes(x = 1, y = 29, xend = 1, yend = 30)) + 
  geom_segment(size = .8,
               aes(x = 5, y = 29, xend = 5, yend = 30))
```

### Summary four models

```{r summary}
## Create multipanel Figure 4
## -----------------------------------------------------------------------------
fig4 = Fig_4A + Fig_4B + Fig_4C + Fig_4D + plot_annotation(tag_levels = 'a') & 
  theme(plot.tag = element_text(size = 16, face = "bold"))
fig4

ggsave(fig4,filename = "./Figs/Fig4_predicted_physio_param_infection_intensities.png",units = "px", width = 3700, height = 3700)

## Table 2 
## ----------------------------------------------------------------------------- 
sjPlot::tab_model(
  lmer_br_para,
  lmer_bt_para,
  lmer_bc_para,
  lmer_gr_para,
  show.ci50 = T ,
  show.stat = T,
  string.stat = "t",
  p.val = "kr",
  show.df = T,
  dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
  file = "./Tables/Table2_results_parasitemia_lmer_physiological_parameters_p.val_kr.html")
```

## Host health to parasitemia 

```{r, warning=F,message=F}
# Results presented in Table 2

## Infection intensity as numerical variable
## -----------------------------------------------------------------------------
tol_resdata <- df %>% 
  mutate(Infection_intensity.2 = as.numeric(Infection_intensity.2)) %>% 
  mutate(Diff_Inf_Class = factor(Diff_Inf_Class, levels = c("Increase","Peak","Decrease")))

## Modeling host health to Infection intensity
## -----------------------------------------------------------------------------
lm(delta_body_condition~Infection_intensity.2, data = tol_resdata) %>%
summary()

## Modeling host health to Infection intensity : Infection stages
## -----------------------------------------------------------------------------
tolres_deltamod = lm(delta_body_condition ~ Infection_intensity.2*Diff_Inf_Class,
                     data = tol_resdata)
summary(tolres_deltamod)

## Comparison of intercepts
## -----------------------------------------------------------------------------
emm = emmeans(tolres_deltamod, "Diff_Inf_Class", at = list(Infection_intensity.2 = 0))
pairs(emm)

## Pairwise comparison of slopes
## -----------------------------------------------------------------------------
lms_delta = lstrends(tolres_deltamod, ~ Diff_Inf_Class:Infection_intensity.2,
                     var = "Infection_intensity.2")
contrast(lms_delta,"pairwise")

## Comparison of slopes to zero
## -----------------------------------------------------------------------------

summary(lms_delta, infer = T)

## Plotting body condition change with the interaction second infection intensity - infection stage
## -----------------------------------------------------------------------------
tolres <- 
  ggplot(data = filter(df, !Infection_intensity.2 %in% c(NA,0), !Diff_Inf_Class %in% NA),
         aes(y = delta_body_condition, x = as.numeric(Infection_intensity.2), col = Diff_Inf_Class)) + 
  geom_jitter(size = 3, alpha = 0.5) + 
  geom_smooth(alpha = 0.2, size = 1.5, method = 'lm',se = T, width = 0.2) + 
  facet_wrap(facets = 'Diff_Inf_Class') +
  labs(y = "Body condition change",x = "Parasitemia \n at second sampling",
       col = 'Infection stages') + 
  scale_x_continuous(breaks = seq(2,5,1),labels = c("1","2","3","4")) + 
  scale_color_manual(labels = c("Increasing", "Peak", "Decreasing"),
                     values = c("#3B9AB2", "#E1AF00", "#F21A00")) + 
  theme_bw()+
  annotate(geom = 'segment', y = -Inf, yend = Inf, color = 'black', x = Inf, xend = Inf, size = 0.5) +
  annotate(geom = 'segment', y = -Inf, yend = Inf, color = 'black', x = -Inf, xend = -Inf, size = 0.5) +
  theme(legend.position = "none", 
        axis.text = element_text(size = 18), 
        axis.title = element_text(size = 20),
        strip.text = element_text(face = "bold", size = 16))

## Arrange plot for three infection stages 
## -----------------------------------------------------------------------------
g <- ggplot_gtable(ggplot_build(tolres))
stripr <- which(grepl('strip-t', g$layout$name))
fills <- c("#4CC6E5", "#F7C600", "#FF5643")
k <- 1
for (i in stripr) {
 j <- which(grepl('rect', g$grobs[[i]]$grobs[[1]]$childrenOrder))
g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
k <- k + 1
}

g = arrangeGrob(g)

## Saving Figure 3
## -----------------------------------------------------------------------------
fig3 = tolres + 
  theme(plot.tag = element_text(size = 16, face = "bold"))
fig3

ggsave(g,filename = "./Figs/Fig3_delta_body_condition_to_parasitemia_second.png",units = "px", width = 3700, height = 2400)
```

## Supplementary figures

Creating supplementary figures:

```{r}

figS1 <- Fig_S1A + Fig_S1B + Fig_S1C + Fig_S1D + plot_annotation(tag_levels = 'a') & 
  theme(plot.tag = element_text(size = 16, face = "bold"))
figS1

## Plotting observed values across infection stages
## ----------------------------------------------------------------------------- 

ggsave(figS1,filename = "./Figs/FigS1_predicted_physio_param_infection_stages.png",units = "px", width = 3700, height = 3700)


Fig_S2A = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
  aes(Diff_Inf_Class,Breathing_rate) + 
  geom_hline(yintercept = mean(df$Breathing_rate, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Breathing rate") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size = 2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size = 5, show.legend = FALSE) + 
  stat_n_text() +  
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 20),
        axis.text = element_text(size = 16), 
        axis.line.x = element_blank(), 
        axis.ticks.x = element_blank(),
        plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold"))

Fig_S2B = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
  aes(Diff_Inf_Class,body_temperature) + 
  geom_hline(yintercept = mean(df$body_temperature, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Body temperature") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size = 2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size = 5 ,show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none", 
        axis.title = element_text(size = 20), 
        axis.text = element_text(size = 16),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), 
        plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold"))

Fig_S2C = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
  aes(Diff_Inf_Class,delta_body_condition) + 
  geom_hline(yintercept = mean(df$delta_body_condition, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "\U0394 Body condition") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size = 2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size = 5 ,show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none", 
        axis.title = element_text(size = 20), 
        axis.text = element_text(size = 16),
        axis.line.x = element_blank(), 
        axis.ticks.x = element_blank(),
        plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold"))

Fig_S2D = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
  aes(Diff_Inf_Class,Growth_rate) + 
  geom_hline(yintercept = mean(df$Growth_rate, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Growth rate") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size = 2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size = 5 ,show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none", 
        axis.title = element_text(size = 20), 
        axis.text = element_text(size = 16), 
        axis.line.x = element_blank(), 
        axis.ticks.x = element_blank(), 
        plot.margin = margin(0, 0, 0, 0, "cm"), 
        plot.title = element_text(hjust = 0.5, face = "bold"))

## Saving Figure S2
## ----------------------------------------------------------------------------- 
figs2 = Fig_S2A + Fig_S2B + Fig_S2C + Fig_S2D + plot_annotation(tag_levels = 'a') & 
  theme(plot.tag = element_text(size = 16, face = "bold"))
figs2

ggsave(figs2,filename = "./Figs/FigS2_observed_physio_param_infection_stages.png",units = "px", width = 3500, height = 3800)

## Plotting observed values across infection intensities
## ----------------------------------------------------------------------------- 
Fig_S3A = ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
  aes(Infection_intensity.2,Breathing_rate) + 
  geom_hline(yintercept = mean(df$Breathing_rate, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Breathing rate") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size = 2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size = 5, show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 20),
        axis.text = element_text(size = 16),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold"))

Fig_S3B <- ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
  aes(Infection_intensity.2,body_temperature) + 
  geom_hline(yintercept = mean(df$body_temperature, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Body temperature") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size = 2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size = 5, show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 20),
        axis.text = element_text(size = 16), 
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold"))

Fig_S3C = ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
  aes(Infection_intensity.2,delta_body_condition) + 
  geom_hline(yintercept = mean(df$delta_body_condition, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "\U0394 Body condition") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size = 2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size = 5, show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none", 
        axis.title = element_text(size = 20),
        axis.text = element_text(size = 16), 
        axis.line.x = element_blank(), 
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold"))

Fig_S3D = ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
  aes(Infection_intensity.2,Growth_rate) + 
  geom_hline(yintercept = mean(df$Growth_rate, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Growth rate") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size = 2.8, width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size = 5, show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none", 
        axis.title = element_text(size = 20), 
        axis.text = element_text(size = 16),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold"))

## Saving figure S3
## ----------------------------------------------------------------------------- 
figs3 = Fig_S3A + Fig_S3B + Fig_S3C + Fig_S3D + plot_annotation(tag_levels = 'a') & 
  theme(plot.tag = element_text(size = 16, face = "bold"))
figs3

ggsave(figs3,filename = "./Figs/FigS3_observed_physio_param_parasitemia.png",units = "px", width = 3500, height = 3800)

## Plotting effect sizes of 'infection stages' models
## ----------------------------------------------------------------------------- 
Fig_S4A = plot_model(
  lmer_br,
  sort.est = T,
  se = T,
  title = "Breathing rate",
  axis.labels = 
    rev(c("Increase : Treatment [Malarone]","Age (days)",
          "Peak : Treatment [Malarone]","Decrease : Treatment [Malarone]",
          "Uninfected : Treatment [Malarone]","Increasing parasitemia",
          "Sex [Males]","Decreasing parasitemia","Sampling interval",
          "Peak parasitemia","Weight (g)","Ambient temperature",
          "Year [2019]","Year [2018]","Year [2020]")))

Fig_S4B = plot_model(
  lmer_bt,
  sort.est = T,
  se = T,
  title = "Body temperature",
  axis.labels = 
    rev(c("Peak : Treatment [Malarone]","Ambient temperature","Year [2020]",
          "Age (days)","Decrease : Treatment [Malarone]","Weight (g)",
          "Sex [Males]", "Decreasing parasitemia","Increase : Treatment [Malarone]",
          "Increasing parasitemia","Uninfected : Treatment [Malarone]",
          "Peak parasitemia","Sampling interval")))

Fig_S4C = plot_model(
  lmer_bc,
  sort.est = T,
  se = T,
  title = "\U0394 Body condition",
  axis.labels =
    rev(c("Year [2020]","Peak : Treatment [Malarone]","Year [2018]",
          "Year [2019]","Sampling interval","Increase : Treatment [Malarone]",
          "Decrease : Treatment [Malarone]","Age (days)",
          "Uninfected : Treatment [Malarone]","Sex [Males]",
          "Increasing parasitemia","Decreasing parasitemia","Peak parasitemia")))

Fig_S4D = plot_model(
  lmer_gr,
  sort.est = T,
  se = T,
  title = "Growth rate", 
  axis.labels = 
    rev(c("Peak : Treatment [Malarone]","Year [2020]","Year [2018]",
          "Sampling interval","Year [2019]","Decrease : Treatment [Malarone]",
          "Increase : Treatment [Malarone]","Uninfected : Treatment [Malarone]",
          "Increasing parasitemia","Decreasing parasitemia","Peak parasitemia",
          "Sex [Males]","Age (days)")))

## Saving Figure S4
## ----------------------------------------------------------------------------- 
figs4 = Fig_S4A + Fig_S4B + Fig_S4C + Fig_S4D + plot_annotation(tag_levels = 'a') & 
  theme(plot.tag = element_text(size = 16, face = "bold"))
figs4

ggsave(figs4,filename = "./Figs/FigS4_effect_sizes_param_stages.png",units = "px", width = 3500, height = 3800)

## Plotting effect sizes of 'infection intensities' models
## ----------------------------------------------------------------------------- 
Fig_S5A = plot_model(
  lmer_br_para,
  sort.est = T,
  se = T,
  title = "Breathing rate",
  axis.labels = 
    rev(c("Infection intensity [2] : Treatment [Malarone]","Age (days)",
          "Infection intensity 1", "Infection intensity 4",
          "Infection intensity [1] : Treatment [Malarone]",
          "Infection intensity [3] : Treatment [Malarone]",
          "Infection intensity [0] : Treatment [Malarone]",
          "Sex [Males]","Infection intensity 3","Sampling interval",
          "Infection intensity 2","Weight (g)","Ambient temperature",
          "Year [2019]","Year [2018]","Year [2020]")))

Fig_S5B = plot_model(
  lmer_bt_para,
  sort.est = T,
  se = T,
  title = "Body temperature",
  axis.labels = 
    rev(c("Ambient temperature","Year [2020]","Age (days)",
          "Infection intensity [3] : Treatment [Malarone]",
          "Infection intensity 1", "Infection intensity [2] : Treatment [Malarone]",
          "Weight (g)","Infection intensity 2","Sex [Males]",
          "Infection intensity [0] : Treatment [Malarone]",
          "Infection intensity [1] : Treatment [Malarone]",
          "Infection intensity 3", "Sampling interval","Infection intensity 4")))

Fig_S5C = plot_model(
  lmer_bc_para,
  sort.est = T,
  se = T,
  title = "\U0394 Body condition",
  axis.labels = 
    rev(c("Year [2020]","Year [2018]","Year [2019]",
          "Infection intensity [2] : Treatment [Malarone]",
          "Infection intensity 1","Sampling interval",
          "Infection intensity [3] : Treatment [Malarone]",
          "Infection intensity [0] : Treatment [Malarone]",
          "Age (days)","Sex [Males]","Infection intensity 3",
          "Infection intensity 2","Infection intensity [1] : Treatment [Malarone]",
          "Infection intensity 4")))

Fig_S5D = plot_model(
  lmer_gr_para,
  sort.est = T,
  se = T,
  title = "Growth rate", 
  axis.labels = 
    rev(c("Year [2020]","Infection intensity [2] : Treatment [Malarone]",
          "Year [2018]","Year [2019]","Sampling interval","Infection intensity 1",
          "Infection intensity [3] : Treatment [Malarone]",
          "Infection intensity [0] : Treatment [Malarone]",
          "Infection intensity 3","Sex [Males]","Infection intensity 2",
          "Age (days)","Infection intensity 4","Infection intensity [1] : Treatment [Malarone]")))

## Figure S4
## ----------------------------------------------------------------------------- 
figs5 = Fig_S5A + Fig_S5B + Fig_S5C + Fig_S5D + plot_annotation(tag_levels = 'a') & 
  theme(plot.tag = element_text(size = 16, face = "bold"))
figs5

ggsave(figs5, filename = "./Figs/FigS5_effect_sizes_param_intensities.png",units = "px", width = 3500, height = 3800)
```

## Estimating measurment error of body temperature

```{r, message=F, warnings=F}
## Loading repeated temperature measures 
## ----------------------------------------------------------------------------- 
rTemp = read.csv2("./Repeatability_temperatures.csv", h = T, dec = '.') %>% 
  mutate(ID = as.factor(ID)) %>% 
  mutate(Date = as.Date(Date, format = '%d/%m/%y')) %>% 
  mutate(Repeat = as.factor(Repeat))

## Estimating repeatability of paired measures
## -----------------------------------------------------------------------------
rpt(Temperature ~ (1|ID), grname = "ID", data = rTemp, npermut = 1000, datatype = 'Gaussian')

## Estimating the variance of error
## -----------------------------------------------------------------------------
rt = ddply(rTemp,.(ID),summarize, mean = mean(Temperature), sd = sd(Temperature))

## Values of mean and standard deviation of average paired body temperatures
## ----------------------------------------------------------------------------- 
mean(rt$mean)
mean(rt$sd)
```

```{r}
sessionInfo()
```

