---
title: "R code for 'Apparent physiological costs of blood parasite infection in the early-life of a vertebrate host - only in highest infections'"
author: "Tony Rinaud, Meinolf Ottensmann, Oliver Krüger & Nayden Chakarov"
output: html_document
---

This document provides all the `R code` used in our paper. Both the Rmarkdown file and the data can be downloaded from the accompanying GitHub repository on (<https://github.com/TonyRinaud/MS_physiology_infection>) as a zip archive containing all the files. We recommend to download or clone this [GitHub repository](https://github.com/TonyRinaud/MS_physiology_infection) in order to access the documentation together with all the files that are needed to repeat analyses shown in this document. Just click on the link above and then on the green box `Clone or download`. In order to function properly, the same structure of folders must be kept. If you have any questions, don't hesitate to contact [tony.rinaud\@gmail.com](mailto:tony.rinaud@gmail.com){.email}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, strip.white = TRUE, collapse = TRUE, fig.align = "center",
                      warning = F, message = F, highlight = TRUE, tidy = TRUE)

# Routine clean-up upon start

rm(list=ls())
```

## Required packages

A number of packages, all of which are available on CRAN are required to repeat analyses presented in this document. The code chunk below allows to load them for the analyses.

```{r packages, message=F, warning=F}
library(chron)
library(cowplot)
library(EnvStats)
library(lme4)
library(lsmeans)
library(ggalt)
library(ggdist)
library(ggeffects)
library(ggplot2)
library(ggpubr)
library(ggrepel)
library(ggridges)
library(ggsci)
library(ggsignif)
library(grid)
library(gridExtra)
library(magrittr)
library(patchwork)
library(plyr)
library(rptR)
library(RVAideMemoire)
library(sjPlot)
library(sjlabelled)
library(sjmisc)
library(tidybayes)
library(tidyverse)
library(wesanderson)
theme_set(theme_tidybayes() + panel_border())
```

## Load raw data

The raw data is comprised of 276 common buzzard (*Buteo buteo*) individuals. Each individual was sampled twice over the course of nestling period during the years 2016 and 2018 - 2020. First, the raw data is loaded from the file `physiology_infection_stage_full_wideformat.csv` and formatted (scaling variables, reordering factor levels etc.) for downstream analyses

```{r data}
## Load data from csv file and code variable classes
## -----------------------------------------------------------------------------
df <- 
  read.csv('./physiology_infection_stage_full_wideformat.csv', h = T, sep = ';', dec = ".") %>% 
  mutate(Nest = as.factor(Nest)) %>% 
  mutate(Date = chron(as.character(Date), format = "d/m/y")) %>% 
  mutate(Infection_intensity.1 = as.factor(Infection_intensity.1)) %>% 
  mutate(Infection_intensity.2 = as.factor(Infection_intensity.2)) %>%
  mutate(Prevalence2 = as.factor(ifelse(Infection_intensity.2 == 0, 0, 1))) %>%
  mutate(Prevalence1 = as.factor(ifelse(Infection_intensity.1 == 0, 0, 1))) %>% 
  mutate(Breathing_rate = as.numeric(Breathing_rate)) %>% 
  mutate(Sex = as.factor(Sex)) %>% 
  mutate(Sampling_rank = as.factor(Sampling_rank)) %>% 
  mutate(Weight_g = scale(as.numeric(Weight.2))) %>% 
  mutate(Wing_cm = as.numeric(Wing.2)) %>% 
  mutate(body_temperature = as.numeric(body_temperature)) %>% 
  mutate(delta_body_condition = as.numeric(delta_body_condition)) %>% 
  mutate(Ambient_Temperature_AvgC = scale(as.numeric(TemperatureAvgC))) %>% 
  mutate(Treatment = as.factor(Treatment)) %>% 
  mutate(Year = as.factor(Year)) %>% 
  mutate(Growth_rate = as.numeric(Growth_rate)) %>% 
  mutate(days_resample = scale(days_resample)) %>% 
  mutate(Age_in_days = scale(as.numeric(Age_in_days))) %>% 
  mutate(Diff_Inf_Class = factor(Diff_Inf_Class, levels = c("Uninfected","Increase","Peak","Decrease")))
 
## Arrange data frame
## ----------------------------------------------------------------------------- 
df <- arrange(df, df$Diff_Inf_Class)

```

## Effects on parasites

Investigating treatment effects on the prevalence of *Leucocytozoon* parasites:

```{r}
## Build contingency table: Infection prevalence and treatment: First sampling
## -----------------------------------------------------------------------------
pre_treatment <- with(df, table(Prevalence1, Treatment))
prop.test(pre_treatment)
pairwise.prop.test(pre_treatment)

## Build contingency table: Infection prevalence and treatment: Second sampling
## -----------------------------------------------------------------------------
post_treatment <- with(df, table(Prevalence2, Treatment))
prop.test(post_treatment)
pairwise.prop.test(post_treatment)

## Proportion of infected individuals across time points
## -----------------------------------------------------------------------------
infected_treatment <- 
  matrix(c(pre_treatment[2,], post_treatment[2,]), nrow = 2) %>% 
  set_colnames(., c("Pre", "Post")) %>% 
  set_rownames(., c("Control", "Malarone"))
prop.test(infected_treatment)
pairwise.prop.test(infected_treatment)

## Proportion of uninfected individuals across time points
## -----------------------------------------------------------------------------
uninfected_treatment <- 
  matrix(c(pre_treatment[1,], post_treatment[1,]), nrow = 2) %>% 
  set_colnames(., c("Pre", "Post")) %>% 
  set_rownames(., c("Control", "Malarone"))
prop.test(uninfected_treatment)
pairwise.prop.test(uninfected_treatment)


## Plotting count of infected / uninfected nestlings across treatments
## -----------------------------------------------------------------------------
tab_cont = data.frame(
  Count = c(infected_treatment[1,], uninfected_treatment[1,], infected_treatment[2,], uninfected_treatment[2,]),
  Timepoint = rep(c("Pre-treatment","Post-treatment"), 4),
  Treatment = rep(c("Control", "Treatment"), each = 4),
  Prevalence = rep(rep(c("Infected", "Uninfected"), each = 2),2)) %>% 
  mutate(Timepoint = factor(Timepoint, levels = c("Pre-treatment","Post-treatment"))) %>% 
  mutate(Prevalence = factor(Prevalence, levels = c("Uninfected","Infected")))
    
##  Create Figure 2a
## -----------------------------------------------------------------------------
treatment_prevalence_changes  <- ggplot(tab_cont) +  
  aes(Timepoint, Count, fill = Prevalence) +  
  facet_wrap(facets = "Treatment") +  
  geom_bar(stat = 'identity',  width = 0.3) +  
  labs(y = "Count of nestlings") +  
  geom_text(aes(label = Count),position  = position_stack(0.5)) +  
  scale_fill_manual(values = c("#D0D0D0","#A8A8A8")) +  
  theme(axis.title.x  =  element_blank(), 
        strip.text = element_text(size = 16, face = "bold"),
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 16),
        axis.title.y = element_text(size = 18, margin =  unit(c(0, 3, 0, 0), "mm")),
        axis.text = element_text(size = 16))

## Plotting mean infection intensity values of nestlings across treatments
## -----------------------------------------------------------------------------
mean_infint = data.frame(
  Sampling_rank = factor(c(rep("1",length(df$Sampling_rank)),as.character(df$Sampling_rank)),levels = c("1","2"),
                         labels  =  c("Pre-treatment","Post-treatment")),
  Infection_intensity = as.numeric(c(as.character(df$Infection_intensity.1),as.character(df$Infection_intensity))),
  Treatment = factor(c(as.character(rep(df$Treatment,2))),levels  =  c("Control","Malarone")))

## Figure 2b
## -----------------------------------------------------------------------------
treatment_meaninf_changes = ggplot(mean_infint) +
  aes(Sampling_rank, Infection_intensity, group = Treatment) +
  geom_vline(xintercept  =  "Pre-treatment", linetype = "dashed", color = 'darkgrey') +
  geom_vline(xintercept = "Post-treatment", linetype = "dashed", color = 'darkgrey') +
  labs(y = "Mean infection intensity") +
  geom_point(aes(colour = Treatment),position = position_jitterdodge(jitter.height  =  0.1)) +
  stat_summary(fun = mean, geom = "line",size = 2,color = c("lightgrey","black","black","lightgrey")) +
  stat_summary(fun = mean, geom = "point",size = 5) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.04, size = 2) + 
  scale_color_manual(values = c("lightgrey","black")) + 
  theme_classic() + 
  theme(axis.title.x = element_blank(),
        legend.text = element_text(size = 16),
        legend.title = element_text(size = 16),
        axis.title.y = element_text(size = 18, margin =  unit(c(0, 3, 0, 0), "mm")),
        axis.text = element_text(size = 16),
        plot.margin = unit(c(0,0,0,30), "pt"))

## Panel wrapping Fig2 a & b:
## ----------------------------------------------------------------------------- 
Fig2 <- treatment_prevalence_changes + 
  treatment_meaninf_changes +
  plot_annotation(tag_levels = 'A') + 
  theme(plot.tag = element_text(size = 16, face = "bold"))
ggsave(Fig2,filename = "./Figs/efficiency_malarone.png",units = "px", width = 6000, height = 3000)

## Testing for difference in mean infection intensity between Pre and Post treatment
## -----------------------------------------------------------------------------
mean_before_after <- data.frame(
  Ring_no = 
    c(df$Ring_no[df$Sampling_rank %in% 2], df$Ring_no[df$Sampling_rank %in% 2]),
  Infection_intensity = c(as.character(df$Infection_intensity.1), as.character(df$Infection_intensity.2)),
  Treatment = 
    c(as.character(df$Treatment[df$Sampling_rank %in% 2]), as.character(df$Treatment[df$Sampling_rank %in% 2])),
  Timepoint = 
    c(rep("Pre-treatment", times = length(df$Treatment)), rep("Post-treatment", times = length(df$Infection_intensity.2)))) %>% 
  mutate(Treatment = as.factor(Treatment)) %>% 
  mutate(Timepoint = as.factor(Timepoint))

mal = mean_before_after[mean_before_after$Treatment %in% "Malarone",]
ctrl = mean_before_after[mean_before_after$Treatment %in% "Control",]
first = mean_before_after[mean_before_after$Timepoint %in% "Pre-treatment",]

## Pre-treatment difference in parasitic load between Treatments
## -----------------------------------------------------------------------------
perm.t.test(as.numeric(as.character(first$Infection_intensity)) ~ first$Treatment, progress = F)
sd(first$Infection_intensity[first$Treatment %in% "Control"])

## In malarone treated nestlings
## -----------------------------------------------------------------------------
perm.t.test(as.numeric(as.character(mal$Infection_intensity)) ~ mal$Timepoint, progress = F)

# In control nestlings
## -----------------------------------------------------------------------------
perm.t.test(as.numeric(as.character(ctrl$Infection_intensity))~ctrl$Timepoint, progress = F)
```

## Effects on physiology

Exploring effects on physiology of nestlings due to the treatment:


### Breathing rate

No treatment effect on breathing rate!

```{r}
lm_d1 = lm(Breathing_rate ~ Treatment, data = df)
summary(lm_d1)
```

### Body temperature

No treatment effect on body temperature

```{r}
lm_d2 <- lm(body_temperature~Treatment, data = df)
summary(lm_d2)
```

### Body condition change

No treatment effect on body condition change

```{r}
lm_d3 <- lm(delta_body_condition~Treatment, data = df)
summary(lm_d3)
```

### Growth rate

No treatment effect on growth rates

```{r}
lm_d4 <- lm(Growth_rate~Treatment, data = df)
summary(lm_d4)

## Create Table S1
## -----------------------------------------------------------------------------
tab_model(
  lm_d1,lm_d2,lm_d3,lm_d4,
  show.reflvl = T,
  show.ci50 = T ,
  show.stat = T,
  string.stat = "t",
  pred.labels = c("Intercept","Treatment [Malarone]"),
  dv.labels = c("Breathing rate","Body temperature", "\U0394 Body condition","Growth rate"),
  file = "./Tables/Physiological_parameters_in_decreasing_control_treated.html")
```


## Infection stages as explanatory variable 

Exploring differences in physiological measures that are associated with the infection stage (increase, peak or decreasing) of tested individuals. 

### Breathing rate

```{r mixed model breathing rate}
## Run model
## ----------------------------------------------------------------------------- 
lmer_br <- lmer(
  Breathing_rate ~ Diff_Inf_Class + Diff_Inf_Class:Treatment + 
    days_resample + Age_in_days + Weight_g + Sex + Ambient_Temperature_AvgC + Year + (1|Nest),
  data = df)

## Obtain predicted values for each infection stage
## -----------------------------------------------------------------------------
mod_br <- get_model_data(lmer_br, type = 'pred', terms = "Diff_Inf_Class") %>% 
   mutate(x = factor(c("Uninfected","Increase","Peak","Decrease"), 
                     levels = c("Uninfected","Increase","Peak","Decrease")))

## Extract sample size for infection stage
## -----------------------------------------------------------------------------
n <- table(df$Diff_Inf_Class[!is.na(df$Breathing_rate)])

## ad sample size as label
## -----------------------------------------------------------------------------
mod_br <- mod_br %>% 
  mutate(x = factor(c(paste0(x,"\nn= ",n)), levels = c(paste0(x,"\nn= ",n))))

## Plotting predicted values across infection stages
## -----------------------------------------------------------------------------
gg1_pred <- ggplot(mod_br) + 
  aes(x,predicted) + 
  geom_hline(yintercept = mean(mod_br$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Breathing rate") + 
  ylim(c(min(mod_br$conf.low) - 1.5,max(mod_br$conf.high) + 1.5)) + 
  geom_errorbar(aes(ymin = mod_br$conf.low,ymax = mod_br$conf.high),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_br$predicted - mod_br$std.error, ymax = mod_br$predicted + mod_br$std.error),
                size = 8, colour = wes_palette("Zissou1",4), width = 0,) + 
  geom_point(color = "black", outlier.shape = NA, size = 2, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.line.x = element_blank(), 
        axis.ticks.x = element_blank(), 
        plot.margin = margin(0, 0, 0, 0, "cm"), 
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8,
  aes(x = 1, y = max(mod_br$conf.high) + 1, xend = 4, yend = max(mod_br$conf.high) + 1)) + 
  geom_text(aes(x = 2.5, y = max(mod_br$conf.high) + 1.5),
  label = "n.s.", size = 5)
```

### Body temperature

```{r mixed model body temp}
## Model 
## -----------------------------------------------------------------------------
lmer_bt = lmer(
  body_temperature ~ Diff_Inf_Class + Diff_Inf_Class:Treatment + Ambient_Temperature_AvgC + 
    days_resample + Age_in_days + Weight_g + Sex + Year + (1|Nest),
  data = df)

## Predicted values for each infection stage
## -----------------------------------------------------------------------------
mod_bt = get_model_data(lmer_bt,type = 'pred',terms = "Diff_Inf_Class") %>%
  mutate(x = factor(c("Uninfected","Increase","Peak","Decrease"),
                    levels = c("Uninfected","Increase","Peak","Decrease")))

# Table with sample sizes specific for body temperature data
n2 = table(df$Diff_Inf_Class[!is.na(df$body_temperature)])

mod_bt <- mod_bt %>% 
  mutate(x = factor(c(paste0(x,"\nn= ",n2)), levels = c(paste0(x,"\nn= ",n2))))

# Plotting predicted values across infection stages
gg2_pred <- ggplot(mod_bt) + 
  aes(x,predicted) + 
  geom_hline(yintercept = mean(mod_bt$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Body temperature") + 
  geom_errorbar(aes(ymin = mod_bt$conf.low,ymax = mod_bt$conf.high),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_bt$predicted - mod_bt$std.error,ymax = mod_bt$predicted + mod_bt$std.error),
                size = 8,colour = wes_palette("Zissou1",4), width = 0) + 
  geom_point(color = "black", outlier.shape = NA, size = 2, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title.y = element_text(size = 14, margin = unit(c(0,3,0,0),"mm")), 
        axis.text = element_text(size = 12),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8,
                 aes(x = 1, y = 40.6, xend = 4, yend = 40.6)) + 
    geom_text(aes(x = 2.5, y = 40.7),
              label = "n.s.", size = 5)
```

### Body condition change

```{r mixed model body condition}
## Model 
## -----------------------------------------------------------------------------
lmer_bc <- lmer(
  delta_body_condition ~ Diff_Inf_Class+Diff_Inf_Class:Treatment+days_resample + 
    Age_in_days+Sex+Year+(1|Nest),
  data = df)

# Predicted values for each infection stage
mod_bc = get_model_data(lmer_bc,type = 'pred',terms = "Diff_Inf_Class") %>%
  mutate(x = factor(c("Uninfected","Increase","Peak","Decrease"), 
                  levels = c("Uninfected","Increase","Peak","Decrease")))

# Table with sample sizes specific for body condition change data
n3 = table(df$Diff_Inf_Class[!is.na(df$delta_body_condition)])

mod_bc <- mod_bc %>% 
  mutate(x = factor(c(paste0(x,"\nn= ",n3)), levels = c(paste0(x,"\nn= ",n3))))

# Plotting predicted values across infection stages

gg3_pred = ggplot(mod_bc) + 
  aes(x,predicted) + 
  geom_hline(yintercept = mean(mod_bc$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Δ Body condition") + 
  geom_errorbar(aes(ymin = mod_bc$conf.low,ymax = mod_bc$conf.high),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_bc$predicted - mod_bc$std.error,ymax = mod_bc$predicted + mod_bc$std.error),
                size = 8,colour = wes_palette("Zissou1",4), width = 0,) + 
  geom_point(color = "black", outlier.shape = NA, size = 2, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8, aes(x = 1, y = max(mod_bc$conf.high) + 17, xend = 4, yend = max(mod_bc$conf.high) + 17)) + 
  geom_text(aes(x = 2.5, y = max(mod_bc$conf.high) + 23),
              label = "n.s.", size = 5)
```

### Growth rate

```{r mixed model growth rate}
# Model 
lmer_gr = lmer(Growth_rate ~ Diff_Inf_Class + Diff_Inf_Class:Treatment + Sex + days_resample + Age_in_days + Year + (1|Nest), data= df)

# Predicted values for each infection stages
mod_gr = get_model_data(lmer_gr,type = 'pred',terms = "Diff_Inf_Class") %>%
  mutate(x = factor(c("Uninfected","Increase","Peak","Decrease"), levels = c("Uninfected","Increase","Peak","Decrease")))

# Table with sample sizes specific for growth rate data
n4 = table(df$Diff_Inf_Class[!is.na(df$Growth_rate)])

mod_gr <- mod_gr %>% 
  mutate(x = factor(c(paste0(x,"\nn= ",n4)), levels = c(paste0(x,"\nn= ",n4))))

# Plotting predicted values across infection stages

gg4_pred = ggplot(mod_gr) + 
  aes(x,predicted) + 
  geom_hline(yintercept = mean(mod_gr$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Growth rate") + 
  geom_errorbar(aes(ymin = mod_gr$conf.low,ymax = mod_gr$conf.high),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_gr$predicted - mod_gr$std.error,ymax = mod_gr$predicted + mod_gr$std.error), 
                size = 8,colour = wes_palette("Zissou1",4), width = 0,) + 
  geom_point(color = "black", outlier.shape = NA, size = 2, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none", 
        axis.title.y = element_text(size = 14, margin = unit(c(0, 3, 0, 0), "mm")),
        axis.text = element_text(size = 12),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.margin = margin(0, 0, 0, 30, "pt"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8, aes(x = 1, y = max(mod_gr$conf.high) + 1.2, xend = 4, yend = max(mod_gr$conf.high) + 1.2)) + 
    geom_text(aes(x = 2.5, y = max(mod_gr$conf.high) + 2),
              label = "n.s.", size = 5)
```

## Summarise models

The code below is used to summarise the model output and create Figure 4 and Table 3 as shown in the manuscript.

```{r}
## Figure 4 
## -----------------------------------------------------------------------------
fig4 <- gg1_pred + gg2_pred + gg3_pred + gg4_pred + plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(size = 16, face = "bold"))
ggsave(fig4,filename = "./Figs/predicted_physio_param_infection_stages.png",units = "px", width = 3700, height = 3700)

# Table 3
## -----------------------------------------------------------------------------
sjPlot::tab_model(
  lmer_br,lmer_bt,lmer_bc,lmer_gr,
  show.ci50 = T ,
  show.stat = T,
  string.stat = "t",
  df.method = "kr",
  dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
  file = "./Tables/Table_results_lmer_physiological_parameters_p.val_kr.html")
```

## Parasitemia as explanatory variable

Exploration of effects by parasitemia levels on physiology of individuals.

### Breathing rate

```{r mixed model breathing rate 2}
## Model 
## -----------------------------------------------------------------------------
lmer_br_para = lmer(
  Breathing_rate ~ Infection_intensity.2 + Infection_intensity.2:Treatment + days_resample + 
    Age_in_days + Weight_g + Sex + Ambient_Temperature_AvgC + Year + (1|Nest), data= df)

# Predicted values for post-treament parasitemia 

mod_br_para=get_model_data(lmer_br_para,type = 'pred',terms = "Infection_intensity.2") %>% 
   mutate(x = factor(c("0","1","2","3","4"), levels = c("0","1","2","3","4")))

# Table with sample sizes specific for breathing rate change data

m1 = table(df$Infection_intensity.2[!is.na(df$Breathing_rate)])

mod_br_para <- mod_br_para %>% 
  mutate(x = factor(c(paste0(x,"\nn= ",m1)), levels = c(paste0(x,"\nn= ",m1))))
mod_br_para$lower_CI= c(31.11, mod_br_para$predicted[1] - 2.96, mod_br_para$predicted[1] - 6.49,mod_br_para$predicted[1] - 4.67, mod_br_para$predicted[1] - 4.63)
mod_br_para$higher_CI= c(41.42,mod_br_para$predicted[1]+3.90,mod_br_para$predicted[1]+1.75,mod_br_para$predicted[1]+1.46,mod_br_para$predicted[1]+4.45)
mod_br_para$se= c(2.61,1.74,2.09,1.56,2.31)

# Plotting predicted values across infection intensities

gg1_pred_para = ggplot(mod_br_para) + 
  aes(as.factor(mod_br_para$x),mod_br_para$predicted) + 
  geom_hline(yintercept = mean(mod_br_para$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Breathing rate") + 
  geom_errorbar(aes(ymin = mod_br_para$lower_CI,ymax = mod_br_para$higher_CI),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_br_para$predicted - mod_br_para$se, ymax = mod_br_para$predicted + mod_br_para$se),
                size = 8, colour = wes_palette("Zissou1",5), width = 0,) + 
  geom_point(color = "black", size = 4) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8, aes(x = 1, y = max(mod_br_para$higher_CI, na.rm = T) + 1.2,
                              xend=5, yend = max(mod_br_para$higher_CI, na.rm = T) + 1.2)) + 
    geom_text(aes(x = 3, y = max(mod_br_para$higher_CI, na.rm = T) + 2),
              label = "n.s.", size = 5)
```

### Body temperature

```{r  mixed model body temperature 2, warning=FALSE, message=F, echo=T}
# Model 

lmer_bt_para = lmer(
  body_temperature ~ Infection_intensity.2 + Infection_intensity.2:Treatment + days_resample +
    Ambient_Temperature_AvgC + Age_in_days + Weight_g + Sex + Year + (1|Nest), data= df)

# Predicted values for post-treament parasitemia

mod_bt_para = get_model_data(lmer_bt_para, 
                             type = 'pred',
                             terms = "Infection_intensity.2") %>% 
   mutate(x = factor(c("0","1","2","3","4"), levels = c("0","1","2","3","4")))

# Table with sample sizes specific for body temperature change data

m2 = table(df$Infection_intensity.2[!is.na(df$body_temperature)])

mod_bt_para <- mod_bt_para %>% 
  mutate(x = factor(c(paste0(x,"\nn= ",m2)), levels = c(paste0(x,"\nn= ",m2))))
mod_bt_para$lower_CI= c(39.40,mod_bt_para$predicted[1] - 0.40,mod_bt_para$predicted[1] - 0.60,mod_bt_para$predicted[1] - 0.65,mod_bt_para$predicted[1] - 1.38)
mod_bt_para$higher_CI= c(40.40,mod_bt_para$predicted[1]+0.55,mod_bt_para$predicted[1]+0.36,mod_bt_para$predicted[1]+0.19,mod_bt_para$predicted[1]+(-0.24))
mod_bt_para$se= c(0.23,0.24,0.24,0.21,0.29)

# Plotting predicted values across infection intensities

gg2_pred_para = ggplot(mod_bt_para) + 
  aes(as.factor(mod_bt_para$x),mod_bt_para$predicted) + 
  geom_hline(yintercept = mean(mod_bt_para$predicted, na.rm = T), linetype = "dashed") + 
  geom_errorbar(aes(ymin = mod_bt_para$lower_CI,ymax = mod_bt_para$higher_CI),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_bt_para$predicted - mod_bt_para$se,ymax = mod_bt_para$predicted + mod_bt_para$se),
                size =8,colour = wes_palette("Zissou1",5), width = 0,) + 
  labs(x = "", y = "Body temperature") + 
  geom_point(color = "black", size =4) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.line.x = element_blank(), 
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8, aes(x = 1, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.2,
                              xend = 5, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.2)) + 
    geom_text(aes(x = 3, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.25),
              label = "**", size = 8) + 
  geom_segment(size = .8,
                 aes(x = 1, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.2, xend=1, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.05)) + 
  geom_segment(size = .8,
                 aes(x =5, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.05, xend=5, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.2))
```

### Body condition change

```{r mixed model body condition change 2}
# Model 
lmer_bc_para <- lmer(
  delta_body_condition ~ Infection_intensity.2 + Infection_intensity.2:Treatment + days_resample +
    Age_in_days + Sex + Year + (1|Nest), data= df)

# Predicted values for post-treament parasitemia

mod_bc_para=get_model_data(lmer_bc_para,type = 'pred',terms = "Infection_intensity.2") %>% 
   mutate(x = factor(c("0","1","2","3","4"), levels = c("0","1","2","3","4")))

# Table with sample sizes specific for body condition change data

m3 = table(df$Infection_intensity.2[!is.na(df$delta_body_condition)])

mod_bc_para <- mod_bc_para %>% 
  mutate(x = factor(c(paste0(x,"\nn= ",m3)), levels = c(paste0(x,"\nn= ",m3))))
mod_bc_para$lower_CI= c(-65.99,mod_bc_para$predicted[1] - 5.71,mod_bc_para$predicted[1] - 53.27,mod_bc_para$predicted[1] - 37.05,mod_bc_para$predicted[1] - 71.88)
mod_bc_para$higher_CI= c(25.59,mod_bc_para$predicted[1]+51.67,mod_bc_para$predicted[1]+16.43,mod_bc_para$predicted[1]+16.17,mod_bc_para$predicted[1]+4.09)
mod_bc_para$se= c(23.20,14.57,17.69,13.51,19.29)

# Plotting predicted values across infection intensities

gg3_pred_para = ggplot(mod_bc_para) + 
  aes(as.factor(mod_bc_para$x),mod_bc_para$predicted) + 
  geom_hline(yintercept = mean(mod_bc_para$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Δ Body condition") + 
  geom_errorbar(aes(ymin = mod_bc_para$lower_CI,ymax = mod_bc_para$higher_CI),colour = "black",size = 2, width =.1) + 
  geom_errorbar(aes(ymin = mod_bc_para$predicted-mod_bc_para$se,ymax = mod_bc_para$predicted+mod_bc_para$se),size =8,colour = wes_palette("Zissou1",5), width = 0,) + 
  geom_point(color = "black", size =4) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),  
        axis.text = element_text(size = 12), 
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8,
                 aes(x = 1, y =-105, xend=5, yend =-105)) + 
    geom_text(aes(x =3, y =-110),
              label= "p=0.08", size = 5) + 
  geom_segment(size = .8,
                 aes(x = 1, y =-105, xend=1, yend =-105+5)) + 
  geom_segment(size = .8,
                 aes(x =5, y =-105, xend=5, yend =-105+5))
```

### Growth rate

```{r mixed model growth rate 2}
# Model 
lmer_gr_para = lmer(
  Growth_rate ~ Infection_intensity.2 + Infection_intensity.2:Treatment +
    days_resample + Sex + Age_in_days + Year + (1|Nest), data= df)

# Predicted values for post-treament parasitemia
mod_gr_para=get_model_data(lmer_gr_para,type = 'pred',terms = "Infection_intensity.2") %>% 
   mutate(x = factor(c("0","1","2","3","4"), levels = c("0","1","2","3","4")))

# Table with sample sizes specific for growth rate data

m4 = table(df$Infection_intensity.2[!is.na(df$Growth_rate)])

mod_gr_para <- mod_gr_para %>% 
  mutate(x = factor(c(paste0(x,"\nn= ",m4)), levels = c(paste0(x,"\nn= ",m4))))
mod_gr_para$lower_CI= c(11.44,mod_gr_para$predicted[1] - 2.22,mod_gr_para$predicted[1] - 10.47,mod_gr_para$predicted[1] - 6.60,mod_gr_para$predicted[1] - 11.39)
mod_gr_para$higher_CI= c(25.14,mod_gr_para$predicted[1]+7.08,mod_gr_para$predicted[1]+0.92,mod_gr_para$predicted[1]+1.91,mod_gr_para$predicted[1]+0.89)
mod_gr_para$se= c(3.47,2.36,2.89,2.16,3.12)

# Plotting predicted values across infection intensities

gg4_pred_para = ggplot(mod_gr_para) + 
  aes(as.factor(mod_gr_para$x),mod_gr_para$predicted) + 
  geom_hline(yintercept = mean(mod_gr_para$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Growth rate") + 
  geom_errorbar(aes(ymin = mod_gr_para$lower_CI,ymax = mod_gr_para$higher_CI),colour = "black",size = 2, width =.1) + 
  geom_errorbar(aes(ymin = mod_gr_para$predicted-mod_gr_para$se,ymax = mod_gr_para$predicted+mod_gr_para$se),size =8,colour = wes_palette("Zissou1",5), width = 0,) + 
  geom_point(color = "black", outlier.shape = NA, size =4, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none", 
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8,
                 aes(x = 1, y =5, xend=5, yend =5)) + 
    geom_text(aes(x =3, y =5-0.63),
              label= "p=0.09", size = 5) + 
  geom_segment(size = .8,
                 aes(x = 1, y =5, xend=1, yend =5+0.5)) + 
  geom_segment(size = .8,
                 aes(x =5, y =5, xend=5, yend =5+0.5))

```

### Summary four models

```{r summary}
# Figure 5
fig5=gg1_pred_para+gg2_pred_para+gg3_pred_para+gg4_pred_para + plot_annotation(tag_levels = 'A')& 
  theme(plot.tag = element_text(size = 16, face = "bold"))

ggsave(fig5,filename = "./Figs/predicted_physio_param_infection_intensities.png",units = "px", width = 3700, height = 3700)

# Table 4 

sjPlot::tab_model(lmer_br_para,lmer_bt_para,lmer_bc_para,lmer_gr_para,
                  show.ci50 = T ,
                  show.stat = T,
                  string.stat = "t",
                  p.val = "kr",
                  dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
                  file = "./Tables/table_results_parasitemia_lmer_physiological_parameters_p.val_kr.html")

```

## Host health to parasitemia 

```{r, warning=F,message=F}

## Infection intensity as numerical variable
## -----------------------------------------------------------------------------
tol_resdata = df
tol_resdata$Infection_intensity.2 = as.numeric(tol_resdata$Infection_intensity.2)
tol_resdata$Diff_Inf_Class = factor(tol_resdata$Diff_Inf_Class, levels = c("Increase","Peak","Decrease"))

## Modeling host health to Infection intensity
## -----------------------------------------------------------------------------
tolres_mod=lm(delta_body_condition~Infection_intensity.2, data=tol_resdata)

summary(tolres_mod)

## Modeling host health to Infection intensity : Infection stages
## -----------------------------------------------------------------------------
tolres_deltamod=lm(delta_body_condition~Infection_intensity.2*Diff_Inf_Class, data=tol_resdata)

## Comparison of intercepts
## -----------------------------------------------------------------------------
emm=emmeans(tolres_deltamod, "Diff_Inf_Class", at=list(Infection_intensity.2=0))

pairs(emm)

## Pairwise comparison of slopes
## -----------------------------------------------------------------------------
lms_delta=lstrends(tolres_deltamod,~Diff_Inf_Class:Infection_intensity.2, var= "Infection_intensity.2")

contrast(lms_delta,"pairwise")

## Comparison of slopes to zero
## -----------------------------------------------------------------------------
tolre_deltasum=summary(lms_delta)

summary(lms_delta, infer=T)

## Plotting body condition change with the interaction second infection intensity - infection stage
## -----------------------------------------------------------------------------

tolres <- ggplot(data = df[!df$Infection_intensity.2 %in% c(NA,0) & !df$Diff_Inf_Class %in% NA,],
                aes(y = delta_body_condition, x = as.numeric(Infection_intensity.2), col = Diff_Inf_Class)) + 
    geom_jitter(size = 3, alpha=0.5) + 
    geom_smooth(alpha = 0.2, size =1.5, method='lm',se = T, width=0.2) + 
    facet_wrap(facets = 'Diff_Inf_Class')+
    labs(y = "Body condition change",x = "Parasitemia \n at second sampling", col='Infection stages') + 
    scale_x_continuous(breaks=seq(2,5,1),labels= c("1","2","3","4")) + 
    scale_color_manual(labels = c("Increasing", "Peak", "Decreasing"),values = c("#3B9AB2", "#E1AF00", "#F21A00")) + 
    theme_pubr() +
    annotate(geom = 'segment', y = -Inf, yend = Inf, color = 'black', x = Inf, xend = Inf, size = 0.5) +
    annotate(geom = 'segment', y = -Inf, yend = Inf, color = 'black', x = -Inf, xend = -Inf, size = 0.5) +
    theme(legend.position = "none", 
          legend.text = element_text(size =19),
          legend.title = element_text(size =22), 
          axis.text = element_text(size =16), 
          axis.title = element_text(size =18),
          strip.text = element_text(face="bold", size=14))

g <- ggplot_gtable(ggplot_build(tolres))
stripr <- which(grepl('strip-t', g$layout$name))
fills <- c("#3B9AB2", "#E1AF00", "#F21A00")
k <- 1
for (i in stripr) {
 j <- which(grepl('rect', g$grobs[[i]]$grobs[[1]]$childrenOrder))
g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
k <- k+1
}

g=arrangeGrob(g)

## Saving Figure 3
## -----------------------------------------------------------------------------

fig3=tolres + 
  theme(plot.tag = element_text(size = 16, face = "bold"))

ggsave(g,filename = "./Figs/delta_body_condition_to_parasitemia_second.png",units = "px", width = 3700, height = 2800)
```

## Supplementary figures

Creating supplementary figures:

```{r}
## Plotting observed values across infection stages
## ----------------------------------------------------------------------------- 

gg1 = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
  aes(Diff_Inf_Class,Breathing_rate) + 
  geom_hline(yintercept = mean(df$Breathing_rate, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Breathing rate") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size =2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size =5 ,show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none", axis.title = element_text(size = 14),  axis.text = element_text(size = 12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face = "bold"))

gg2 = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
  aes(Diff_Inf_Class,body_temperature) + 
  geom_hline(yintercept = mean(df$body_temperature, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Body temperature") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size =2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size =5 ,show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none", axis.title = element_text(size = 14),  axis.text = element_text(size = 12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face = "bold"))

gg3 = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
  aes(Diff_Inf_Class,delta_body_condition) + 
  geom_hline(yintercept = mean(df$delta_body_condition, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "\U0394 Body condition") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size =2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size =5 ,show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none", axis.title = element_text(size = 14),  axis.text = element_text(size = 12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face = "bold"))

gg4 = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
  aes(Diff_Inf_Class,Growth_rate) + 
  geom_hline(yintercept = mean(df$Growth_rate, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Growth rate") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size =2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size =5 ,show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none", axis.title = element_text(size = 14),  axis.text = element_text(size = 12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face = "bold"))

## Saving Figure S1
## ----------------------------------------------------------------------------- 

figs1=gg1+gg2+gg3+gg4 + plot_annotation(tag_levels = 'A')& 
  theme(plot.tag = element_text(size = 16, face = "bold"))

ggsave(figs1,filename = "./Figs/observed_physio_param_infection_stages.png",units = "px", width = 3500, height = 3800)

## Plotting observed values across infection intensities
## ----------------------------------------------------------------------------- 

gg5 = ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
  aes(Infection_intensity.2,Breathing_rate) + 
  geom_hline(yintercept = mean(df$Breathing_rate, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Breathing rate") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size =2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size =5 ,show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold"))

gg6 <- ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
  aes(Infection_intensity.2,body_temperature) + 
  geom_hline(yintercept = mean(df$body_temperature, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Body temperature") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size =2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size =5 ,show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12), 
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold"))

gg7 = ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
  aes(Infection_intensity.2,delta_body_condition) + 
  geom_hline(yintercept = mean(df$delta_body_condition, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "\U0394 Body condition") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size =2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size =5 ,show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none", 
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12), 
        axis.line.x = element_blank(), 
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold"))

gg8 = ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
  aes(Infection_intensity.2,Growth_rate) + 
  geom_hline(yintercept = mean(df$Growth_rate, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Growth rate") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size =2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size =5 ,show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none", axis.title = element_text(size = 14),  axis.text = element_text(size = 12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face = "bold"))

## Saving figure S2
## ----------------------------------------------------------------------------- 

figs2=gg5+gg6+gg7+gg8 + plot_annotation(tag_levels = 'A')& 
  theme(plot.tag = element_text(size = 16, face = "bold"))

ggsave(figs2,filename = "./Figs/observed_physio_param_parasitemia.png",units = "px", width = 3500, height = 3800)


## Plotting effect sizes of 'infection stages' models
## ----------------------------------------------------------------------------- 

pm1=plot_model(lmer_br,
               sort.est = T,
               se = T,
               title = "Breathing rate",
               axis.labels = rev(c("Increase : Treatment [Malarone]","Age (days)","Peak : Treatment [Malarone]","Decrease : Treatment [Malarone]","Uninfected : Treatment [Malarone]","Increasing parasitemia","Sex [Males]","Decreasing parasitemia","Sampling interval","Peak parasitemia","Weight (g)","Ambient temperature","Year [2019]","Year [2018]","Year [2020]")))

pm2=plot_model(lmer_bt,
               sort.est = T,
               se = T,
               title = "Body temperature",
               axis.labels = rev(c("Peak : Treatment [Malarone]","Ambient temperature","Year [2020]","Age (days)","Decrease : Treatment [Malarone]","Weight (g)","Sex [Males]",
"Decreasing parasitemia","Increase : Treatment [Malarone]","Increasing parasitemia","Uninfected : Treatment [Malarone]",
"Peak parasitemia","Sampling interval")))

pm3=plot_model(lmer_bc,
               sort.est = T,
               se = T,
               title = "\U0394 Body condition",
               axis.labels = rev(c("Year [2020]","Peak : Treatment [Malarone]","Year [2018]","Year [2019]","Sampling interval","Increase : Treatment [Malarone]","Decrease : Treatment [Malarone]","Age (days)", "Uninfected : Treatment [Malarone]","Sex [Males]","Increasing parasitemia","Decreasing parasitemia","Peak parasitemia")))

pm4=plot_model(lmer_gr,
               sort.est = T,
               se = T,
               title = "Growth rate", 
               axis.labels = rev(c("Peak : Treatment [Malarone]","Year [2020]","Year [2018]","Sampling interval","Year [2019]","Decrease : Treatment [Malarone]","Increase : Treatment [Malarone]","Uninfected : Treatment [Malarone]","Increasing parasitemia","Decreasing parasitemia","Peak parasitemia","Sex [Males]","Age (days)")))

## Saving Figure S3
## ----------------------------------------------------------------------------- 
figs3=pm1+pm2+pm3+pm4 + plot_annotation(tag_levels = 'A')& 
  theme(plot.tag = element_text(size = 16, face = "bold"))

ggsave(figs3,filename = "./Figs/effect_sizes_param_stages.png",units = "px", width = 3500, height = 3800)

## Plotting effect sizes of 'infection intensities' models
## ----------------------------------------------------------------------------- 

pm5=plot_model(lmer_br_para,
               sort.est = T,
               se = T,
               title = "Breathing rate",
               axis.labels = rev(c("Infection intensity [2] : Treatment [Malarone]","Age (days)","Infection intensity 1", "Infection intensity 4", "Infection intensity [1] : Treatment [Malarone]","Infection intensity [3] : Treatment [Malarone]", "Infection intensity [0] : Treatment [Malarone]","Sex [Males]","Infection intensity 3","Sampling interval","Infection intensity 2","Weight (g)","Ambient temperature","Year [2019]","Year [2018]","Year [2020]")))

pm6=plot_model(lmer_bt_para,
               sort.est = T,
               se = T,
               title = "Body temperature",
               axis.labels = rev(c("Ambient temperature","Year [2020]","Age (days)", "Infection intensity [3] : Treatment [Malarone]","Infection intensity 1", "Infection intensity [2] : Treatment [Malarone]","Weight (g)","Infection intensity 2","Sex [Males]","Infection intensity [0] : Treatment [Malarone]","Infection intensity [1] : Treatment [Malarone]","Infection intensity 3", "Sampling interval","Infection intensity 4")))

pm7=plot_model(lmer_bc_para,
               sort.est = T,
               se = T,
               title = "\U0394 Body condition",
               axis.labels = rev(c("Year [2020]","Year [2018]","Year [2019]","Infection intensity [2] : Treatment [Malarone]","Infection intensity 1","Sampling interval","Infection intensity [3] : Treatment [Malarone]","Infection intensity [0] : Treatment [Malarone]","Age (days)","Sex [Males]","Infection intensity 3","Infection intensity 2","Infection intensity [1] : Treatment [Malarone]","Infection intensity 4")))

pm8=plot_model(lmer_gr_para,
               sort.est = T,
               se = T,
               title = "Growth rate", 
               axis.labels = rev(c("Year [2020]","Infection intensity [2] : Treatment [Malarone]","Year [2018]","Year [2019]","Sampling interval","Infection intensity 1","Infection intensity [3] : Treatment [Malarone]","Infection intensity [0] : Treatment [Malarone]","Infection intensity 3","Sex [Males]","Infection intensity 2","Age (days)","Infection intensity 4","Infection intensity [1] : Treatment [Malarone]")))

## Figure S4
## ----------------------------------------------------------------------------- 

figs4=pm5+pm6+pm7+pm8 + plot_annotation(tag_levels = 'A')& 
  theme(plot.tag = element_text(size = 16, face = "bold"))

ggsave(figs4,filename = "./Figs/effect_sizes_param_intensities.png",units = "px", width = 3500, height = 3800)
```
## Estimating measurment error of body temperature

```{r, message=F, warnings=F}
## Loading repeated temperature measures 
## ----------------------------------------------------------------------------- 

rTemp=read.csv2("./Repeatability_temperatures.csv", h=T, dec='.')

rTemp$ID=as.factor(rTemp$ID)
rTemp$Date=as.Date(rTemp$Date, format='%d/%m/%y')
rTemp$Repeat=as.factor(rTemp$Repeat)

## Estimating repeatability of paired measures
## -----------------------------------------------------------------------------

rpt(Temperature ~ (1|ID), grname = "ID", data = rTemp, npermut = 1000, datatype = 'Gaussian')

## Estimating the variance of error
## -----------------------------------------------------------------------------

rt=ddply(rTemp,.(ID),summarize,mean=mean(Temperature),sd=sd(Temperature))

## Values of mean and standard deviation of average paired body temperatures
## ----------------------------------------------------------------------------- 

mean(rt$mean)
mean(rt$sd)

```

